### 2021-12-12 thesis/tex/conclusion.tex
update

\chapter{Conclusion}\label{ch:conc}
TBD
% TODO Conclusion:
% We produced the conclusion plots, and ic is insensitive to any impact if th34.
% NSI: which detector is more sensitive? Add paragraph on what parameters that PINGU can measure (in future tense). Write what constrain which parameters?
% Include effect on system uncertainty on PINGU. Compare with other measurements. Write from fig 5.7 that let Eem are anti-correlated, while no significant correlation can be seen from emt-emt, emt-eet.
% Reference papers on PINGU, NSI. And NSI from Llong baseline experiments. Include reference to DUNE from ESS paper with S+T+M.

>>>>

\chapter{Conclusion}\label{ch:conc}
We were able to simulate the IceCube experiment with 86 strings, with the event count of our $3+0$ hypothesis shown against the IceCube Monte Carlo in Fig.~\ref{fig:IC_MC_norm}. 
We normalized against the Monte Carlo, and produced the exclusion contour between the sterile neutrino parameters $\dm[41]$ and $\theta_{24}$ in Fig.~\ref{fig:error_tuning}.
We found that the data is consistent with the $3+0$ hypothesis, with deviations up to 6\% at $\SI{10}{\TeV}$.
Our best-fit parameters were found to be $\dm[41] = \SI{0.01}{\eV^2}$ and $\theta_{24} = 0.67$ ($\sin^22\theta_{24} = 0.95$) at 
a p-value of $33\%$.
We also investigated the case when $\theta_{24} = \theta_{34}$, and which produced an identical exclusion contour as in the case with $\theta_{34}=0$. From this observation, 
we conclude that IceCube is currently insensitive to any impact of $\theta_{34}$, with track events alone. However,
when opening up the $\tau$ channel by allowing $\theta_{34} \neq 0$, it is possible that with an inclusion of cascade events from $\nt$, IceCube could be able to better observe 
an impact of $\theta_{34}$.

In our second part of the work, we put the sterile neutrino completely aside, and turned our focus to non-standard interactions. 
We included DeepCore in order to both lower the energy range of the data, but also to include cascade events in this range. 
Additionally, we simulated a proposed upgrade to DeepCore, PINGU, and produced data for it assuming a standard $3+0$ hypothesis with parameters from~\cite{nufit}.
We saw that, on a probability level, in the high energy region of IceCube, NSI effects other than those stemming from $\emt$ are not apparent.
Moreover, we saw in the $\Pme$ shown in Fig~\ref{fig:eem_eet_prob} that we could expect a correlation between $\eem$ and $\eet$ in the single-digit \si{\GeV} range.
We also saw that $\emt$ effects were visible on probability level in both the \si{\GeV} and \si{\TeV} regions, making us hope to constrain $\emt$ further by 
a joint analysis. This suspicion was confirmed in Fig.~\ref{fig:IC_3D} and shown in Eq.~\ref{eq:PID_result}, where we obtained a stringent bound on $\emt$:
\begin{align}
    -0.010 <&\, \emt < 0.0060\,,
 \end{align}
Thus, we expect PINGU to successfully be able to observe the impact of NSI, and a joint analysis between PINGU and at least one of the other detectors under the IceCube collaboration
will be able to even further constrain the parameters.

Our parameters obtained from the DeepCore analysis was more stringent than those obtained in~\cite{demidov}, which used the same data sample as us.
These bounds were found to be 
\begin{align}
    -0.054 <&\, \ett < 0.067 \nonumber \\
    -0.029 <&\, \emt < 0.0070 \nonumber \\
    -0.12 <&\, \eem < 0.15 \nonumber \\
    -0.084 <&\, \eet < 0.15\,.
 \end{align}
In Fig~\ref{fig:event_pulls}, we saw that we can expect PINGU to be more sensitive to NSI effects than DeepCore, with $\emt$ effects being the weakest 
due to their low effect on all probability channels in the \si{\GeV} range. Moreover, we saw that when constraining $\eem$ and $\eet$ from the negative side, 
we can expect the result to be highly dependent on the systematic uncertainty of PINGU.

Finally, we saw that the effect on $\eem$ and $\eet$ on $\Pme$ shown in Fig.~\ref{fig:eem_eet_prob}.
After setting $\ett=0$ and marginalizing out $\emt$, this effect is expected to propagate through to the event count of PINGU, 
manifesting as an anti-correlation between the $\eem$ and $\eet$, shown in Fig~\ref{fig:PINGU_2D}. No other pair of NSI parameters were observed to have 
a significant correlation.

### 2021-12-12 thesis/tex/introduction.tex
update

\chapter{Introduction}
There is no reason for us to believe that our current knowledge in particle physics is complete.
The most successful framework -- the Standard Model -- has notable shortcomings. Neither does it
explain why there is something rather than nothing\footnote{In the Standard Model,
matter and antimatter come in pairs of one particle and one antiparticle. When interacting,
antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe today contains matter,
there must have been more matter than antimatter at the Big Bang. This baryon asymmetry is unexplained in the Standard 
Model.}, nor does it give a candidate for dark matter
\footnote{Dark matter is heavy matter which does not interact with electromagnetic radiation.
No such particle exists in the Standard Model.}.
To make matters even worse, three of the particles which are massless according to the Standard Model have been observed to have mass.
In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 
We then compare the effects of these extensions with collected data to see if our new theory more closely describes Nature or not.

@@

\section{Outline}
This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts of the Standard Model that will be relevant for our extensions of it.
Then we present the evidence and subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel physics prize, along with the modifications to the Standard Model needed to accommodate the discovery.
The reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix and oscillation Hamiltonian, including the matter effects stemming from charged and neutral current weak interactions within the Earth.

>>>>

\chapter{Introduction}
There is no reason for us to believe that our current knowledge in particle physics is complete.
The most successful framework -- the Standard Model -- has notable shortcomings. Neither does it
explain why there is something rather than nothing\footnote{In the Standard Model,
matter and antimatter come in pairs of one particle and one antiparticle. When interacting,
antimatter \emph{annihilates} the matter, resulting in pure light. Since the universe today contains matter,
there must have been more matter than antimatter at the Big Bang. This baryon asymmetry is unexplained in the Standard 
Model.}, nor does it give a candidate for dark matter\footnote{Dark matter is heavy matter which does not interact with electromagnetic radiation.
No such particle exists in the Standard Model.}.
To make matters even worse, three of the particles which are massless according to the Standard Model have been observed to have mass.
In this thesis, we focus on the said particles -- the neutrinos -- and propose extensions to the Standard Model related to them. 
We then compare the effects of these extensions with collected data to see if our new theory more closely describes Nature or not.

@@

\section{Outline}
This thesis is outlined as follows. In Chapter~\ref{ch:osc}, we briefly review the most relevant parts of the Standard Model that will be relevant for our extensions of it.
Then we present the evidence and subsequent discovery of neutrino oscillations, which ultimately led to the 2015 Nobel prize in physics, along with the modifications to the Standard Model needed to accommodate the discovery.
The reader is then introduced to a standard but detailed derivation of the neutrino mixing matrix and oscillation Hamiltonian, including the matter effects stemming from charged and neutral current weak interactions within the Earth.
